Appendix

### 2024-09-13 manuscript/manuscript.Rmd
Fixed missing passing of method argument.

The Top Gear dataset contains data on 297 vehicles that appeared on the BBC television show *Top Gear* [@Alfons2021-kc].
Within this dataset, the fuel consumption feature contains outliers due to highly fuel-efficient vehicles.
Applying conventional and invariant Yeo-Johnson transformations to the fuel consumption feature yielded the following results, see Figure \ref{fig:experimental-results-outlier-robustness}:
no transformation (residual sum $\sum r_i = 54$, $p=0.56$);
conventional transformation ($\lambda = -0.1$, $\sum r_i = 55$, $\mu_{YJ} = 3.0$, $\sigma_{YJ} = 0.3$, $p=0.01$);
Raymaekers and Rousseeuw's robust adaptation ($\lambda = 0.8$, $\sum r_i = 48$, $\mu_{YJ} = 29$, $\sigma_{YJ} = 15$, $p=0.55$);
location- and scale-invariant transformation ($\lambda = -1.3$, $\sum r_i = 44$, $\mu_{YJ} = 0.5$, $\sigma_{YJ} = 0.1$, $p=0.03$);
and robust location- and scale-invariant transformation ($\lambda = -0.9$, $\sum r_i = 50$, $\mu_{YJ} = 2.0$, $\sigma_{YJ} = 2.3$, $p=0.58$).

>>>>

The Top Gear dataset contains data on 297 vehicles that appeared on the BBC television show *Top Gear* [@Alfons2021-kc].
Within this dataset, the fuel consumption feature contains outliers due to highly fuel-efficient vehicles.
Applying conventional and invariant Yeo-Johnson transformations to the fuel consumption feature yielded the following results, see Figure \ref{fig:experimental-results-outlier-robustness}:
no transformation (residual sum $\sum r_i = 54$, $p=0.76$);
conventional transformation ($\lambda = -0.1$, $\sum r_i = 55$, $\mu_{YJ} = 3.0$, $\sigma_{YJ} = 0.3$, $p=0.01$);
Raymaekers and Rousseeuw's robust adaptation ($\lambda = 0.8$, $\sum r_i = 48$, $\mu_{YJ} = 29$, $\sigma_{YJ} = 15$, $p=0.55$);
location- and scale-invariant transformation ($\lambda = -1.3$, $\sum r_i = 44$, $\mu_{YJ} = 0.5$, $\sigma_{YJ} = 0.1$, $p=0.03$);
and robust location- and scale-invariant transformation ($\lambda = -0.9$, $\sum r_i = 50$, $\mu_{YJ} = 2.0$, $\sigma_{YJ} = 2.3$, $p=0.58$).

### 2024-09-13 manuscript/manuscript_appendix.Rmd
Fixed missing passing of method argument.

The Top Gear dataset contains data on 297 vehicles, with outliers related highly fuel-efficient vehicles [@Alfons2021-kc].
Applying conventional and invariant Box-Cox transformations to the fuel consumption feature yielded the following results:
no transformation (residual sum $\sum r_i = 54$, $p=0.76$);
conventional transformation ($\lambda = -0.1$, $\sum r_i = 55$, $\mu_{BC} = 3.0$, $\sigma_{BC} = 0.3$, $p=0.01$);
Raymaekers and Rousseeuw's robust adaptation ($\lambda = 0.8$, $\sum r_i = 48$, $\mu_{BC} = 29$, $\sigma_{BC} = 15$, $p=0.55$);
location- and scale-invariant transformation ($\lambda = -1.3$, $\sum r_i = 44$, $\mu_{BC} = 0.5$, $\sigma_{BC} = 0.1$, $p=0.03$);
and robust location- and scale-invariant transformation ($\lambda = 0.9$, $\sum r_i = 49$, $\mu_{BC} = 2.0$, $\sigma_{BC} = 2.3$, $p=0.58$).

@@

The ischemic stroke dataset contains historic data from 126 patients with risk at ischemic stroke [@Kuhn2019-kt].
Applying conventional and invariant Box-Cox transformations to the maximum arterial wall thickness feature yielded the following results:
no transformation (residual sum $\sum r_i = 110$, $p=0.56$);
conventional transformation ($\lambda = -0.7$, $\sum r_i = 30$, $\mu_{BC} = 1.0$, $\sigma_{BC} = 0.1$, $p=0.01$);
Raymaekers and Rousseeuw's robust adaptation ($\lambda = 1.1$, $\sum r_i = 136$, $\mu_{BC} = 7.2$, $\sigma_{BC} = 14$, $p=0.61$);
location- and scale-invariant transformation ($\lambda = 0.2$, $\sum r_i = 12$, $\mu_{BC} = -11.8$, $\sigma_{BC} = 6.9$, $p=0.13$);
and robust location- and scale-invariant transformation ($\lambda = -0.6$, $\sum r_i = 27$, $\mu_{BC} = 0.7$, $\sigma_{BC} = 0.1$, $p=0.10$).

@@

>>>>

The Top Gear dataset contains data on 297 vehicles, with outliers related highly fuel-efficient vehicles [@Alfons2021-kc].
Applying conventional and invariant Box-Cox transformations to the fuel consumption feature yielded the following results:
no transformation (residual sum $\sum r_i = 54$, $p=0.76$);
conventional transformation ($\lambda = -0.1$, $\sum r_i = 55$, $\mu_{BC} = 3.0$, $\sigma_{BC} = 0.3$, $p=0.01$);
Raymaekers and Rousseeuw's robust adaptation ($\lambda = 0.8$, $\sum r_i = 48$, $\mu_{BC} = 29$, $\sigma_{BC} = 15$, $p=0.55$);
location- and scale-invariant transformation ($\lambda = -0.7$, $\sum r_i = 44$, $\mu_{BC} = 0.6$, $\sigma_{BC} = 0.2$, $p=0.02$);
and robust location- and scale-invariant transformation ($\lambda = 1.1$, $\sum r_i = 59$, $\mu_{BC} = 2.4$, $\sigma_{BC} = 1.8$, $p=0.83$).

@@

The ischemic stroke dataset contains historic data from 126 patients with risk at ischemic stroke [@Kuhn2019-kt].
Applying conventional and invariant Box-Cox transformations to the maximum arterial wall thickness feature yielded the following results:
no transformation (residual sum $\sum r_i = 110$, $p=0.56$);
conventional transformation ($\lambda = -0.5$, $\sum r_i = 30$, $\mu_{BC} = 1.0$, $\sigma_{BC} = 0.2$, $p=0.01$);
Raymaekers and Rousseeuw's robust adaptation ($\lambda = 1.1$, $\sum r_i = 136$, $\mu_{BC} = 5.5$, $\sigma_{BC} = 12$, $p=0.60$);
location- and scale-invariant transformation ($\lambda = -1.0$, $\sum r_i = 12$, $\mu_{BC} = 0.7$, $\sigma_{BC} = 0.1$, $p=0.01$);
and robust location- and scale-invariant transformation ($\lambda = 0.5$, $\sum r_i = 27$, $\mu_{BC} = 2.2$, $\sigma_{BC} = 1.4$, $p=0.35$).

@@

# Appendix F: Normalisation before transformation

```{r include = FALSE, eval = TRUE}

data <- .assess_standardisation_before_transformation()
```
